### 2012-04-26 docs/getting_started/getting_started.tex
add example output fig

Visualization and analysis are done on the plotfiles.  A
number of in-house and externally developed tools can work 
with \boxlib-formatted plotfiles.

>>>>

Visualization and analysis are done on the plotfiles.  A number of
in-house and externally developed tools can work
with \boxlib-formatted plotfiles.  An example plot of the {\tt test2}
problem run above is shown in Figure~\ref{fig:gettingstarted:test2}.

\begin{figure}[t]
\centering
\includegraphics[width=3in]{\gsfigpath/plt00133_tfromp}
\caption[Visualization of {\tt test2} output]{\label{fig:gettingstarted:test2} Visualization of the
final output of the {\tt test2} problem showing the temperature
field (as derived from the pressure).  This plot was done with
the {\tt AmrPostprocessing} tools.}
\end{figure}
